---
name: Ross Dahlke
position: "Assistant Professor"
address: "University of Wisconsin-Madison, School of Journalism and Mass Communication"
www: rossdahlke.com
email: "ross.dahlke@wisc.edu"
twitter: ross_dahlke
github: rossdahlke
linkedin: rossdahlke
date: "`r format(Sys.time(), '%B %Y')`"
headcolor: 414141
output:
  vitae::awesomecv:
    pandoc_args: ["--lua-filter=strong.lua", "--lua-filter=reverse-bib-numbers.lua"]
    keep_tex: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
options(tinytex.verbose = TRUE)
options(encoding = "UTF-8")
library(vitae)
library(tidyverse)
```

# Academic Appointments

```{r}
tribble(
  ~ title, ~ year, ~ institution, ~ where, ~ details,
  "Assistant Professor", "2025-Present", "University of Wisconsin-Madison", "Madison, WI", "School of Journalism and Mass Communication",
  "Assistant Professor", "2025-Present", "University of Wisconsin-Madison", "Madison, WI", "Affiliate, Elections Research Center"
) %>% 
  detailed_entries(title, year, institution, where, details)
```

# Education

```{r}
tribble(
  ~ degree, ~ year, ~ institution, ~ where, ~ details,
  "PhD: Communication", "2022-2024", "Stanford University", "Palo Alto, CA", "Dissertation: The Public Sphere in Private Spaces: Politics, News, and Misinformation in Personal Messaging Applications",
  "PhD: Communication", "2022-2024", "Stanford University", "Palo Alto, CA", "Advisor: Jeffrey T. Hancock, Committee: Jennifer Pan, Byron Reeves, Matthew Gentzkow, Michael Bernstein (chair)",
  "PhD: Communication", "2022-2024", "Stanford University", "Palo Alto, CA", "Data Science Scholar, Stanford Data Science Program",
  "PhD: Communication", "2022-2024", "Stanford University", "Palo Alto, CA", "Knight-Hennessy Scholar",
  "MA: Communication", "2020-2022", "Stanford University", "Palo Alto, CA", "Knight-Hennessy Scholar",
  "JBA, Comprehensive Honors (Honors in the Liberal Arts and in the Major) Journalism & Mass Communication; Political Science", "2014-2018", "University of Wisconsin-Madison", "Madison, WI", "Theodore Herfurth Award for top undergraduate male student",
    "JBA, Comprehensive Honors (Honors in the Liberal Arts and in the Major) Journalism & Mass Communication; Political Science", "2014-2018", "University of Wisconsin-Madison", "Madison, WI", "College of Letters & Science Dean's Prize awarded to three students") %>% 
  detailed_entries(degree, year, institution, where, details)
```

# Research

## Publications

\* indicates equal authorship

```{r}
bibliography_entries("../bibliography/publications.bib")
```

## Papers Under Review

\* indicates equal authorship

```{r}
bibliography_entries("../bibliography/working-papers.bib") 
```

## Public Pre-Prints & Reports

```{r}
bibliography_entries("../bibliography/reports.bib")
```

\vspace{1em}
## Invited Talks and Guest Lectures
\vspace{-1em}

```{r}
tribble(
  ~ year, ~ name, ~ event, ~ location,
  '10/2025', "Organizational Communication Mini Conference 2025", "Exploring Ethical Use of AI and Computational Methods in Organizational Research", "University of Illinois Urbana-Champaign",
  '11/2024', "Understanding Election Manipulation with Data Science", "Stanford Democracy Day & Stanford Data Science", "Stanford University",
  '11/2023', "Exposure to Untrustworthy Websites in the 2020 U.S. Presidential Election", "Communication 124/224: Truth, Trust & Technology", "Stanford University",
  '11/2023', "Untrustworthy Website Exposure and Effects", "Stanford Democracy Day & Stanford Data Science", "Stanford University",
  '09/2023', "Single Case Research Methodology and Visualization", "", "University of Minnesota-Twin Cities",
  '05/2022', "Exposure to Untrustworthy Websites in the 2020 U.S. Presidential Election", "Cyber Policy Center, Freeman Spogli Institute", "Stanford University"
) %>%
  detailed_entries(
    when = year,
    what = name,
    with = event,
    where = location
  )
```

# Awards

```{r}
tribble(
  ~ year, ~ name, ~ institution, ~ amount,
  2025, "Collaborative Summer Research Initiative (50% Graduate Project Assistantship)", "University of Wisconsin-Madison Elections Research Center", "$10,700",
  2024, "Top Reviewer Award, 2023", "Social Science Computer Review", "",
  2024, "Non-Western Countries Expanding Online Trust & Safety Research Grant", "Stanford Cyber Policy Center", "$15,000",
  2023, "Data Science Scholar", "Stanford University Data Science", "~$93,000",
  2023, "Stanford EST (Ethics, Society, and Technology) Research Grant", "Stanford University", "$5,000",
  2023, "Stanford PACS (Philantropy and Civil Society) Research Grant", "Stanford University", "$3,000",
  2023, "Graduate Student Researcher", "Office of Army Research & Department of Defense Multidisciplinary University Research Initiative Grant (MURI): Multi-Modal Network Information Dynamics Group", "",
  2020, "Knight-Hennessy Scholarship", "Stanford University", "~$280,000"
) %>%
  detailed_entries(
    when = year,
    what = glue::glue("<name>: <institution> <amount>", .open = "<", .close = ">")
  )
```

# Teaching

```{r}
tribble(
  ~ year, ~ name, ~ duty, ~ institution,
  '01/2026 - 05/2026', "JOURN 677: Concepts and Tools for Data Analysis and Visualization", "Instructor", "University of Wisconsin–Madison",
  '09/2025 - 12/2025', "JOURN 818: Computational Approaches for Communication Research", "Instructor", "University of Wisconsin–Madison",
  '09/2025 - 12/2025', "JOURN 677: Concepts and Tools for Data Analysis and Visualization", "Instructor", "University of Wisconsin–Madison",
  '01/2025 - 05/2025', "JOURN 677: Concepts and Tools for Data Analysis and Visualization", "Instructor", "University of Wisconsin–Madison",
  '03/2024 - 06/2024', "Communication 124/224: Truth, Trust & Technology", "Teaching Assistant", "Stanford University",
  '01/2023 - 03/2023', "Communication 172/272: Media Psychology", "Teaching Assistant", "Stanford University",
  '09/2016 - 05/2018', "Inter-LS 250: Undergraduate Research Experience", "Teaching Fellow", "University of Wisconsin–Madison"
) %>%
  detailed_entries(
    when = year,
    with = name,
    what = duty,
    where = institution
  )
```

## Advising

*PhD Advising*

```{r}
tribble(
  ~ year, ~ name, ~ role, ~ institution,
  '', "Haotian (Barry) Zhao", "", "",
  '', "Yanshu (Sybil) Wang", "", ""
) %>%
  detailed_entries(
    when = year,
    what = name,
    with = role,
    where = institution
  )
```

*Research MA Advising*

```{r}
tribble(
  ~ year, ~ name, ~ role, ~ institution,
  '', "Yingqi (Vicky) Huang", "", ""
) %>%
  detailed_entries(
    when = year,
    what = name,
    with = role,
    where = institution
  )
```

<!--
*Undergraduate Advising*

```{r}
# tribble(
#   ~ year, ~ name, ~ role, ~ institution,
# ) %>%
#   detailed_entries(
#     when = year,
#     with = name,
#     what = role,
#     where = institution
#   )
```
-->

## Directed Study

```{r}
tribble(
  ~ year, ~ name, ~ details, ~ institution,
  'Spring 2026', "Yanshu (Sybil) Wang", "", "",
  'Fall 2025', "Yanshu (Sybil) Wang", "", ""
) %>%
  detailed_entries(
    when = year,
    what = name,
    with = details,
    where = institution
  )
```

<!--
## Committees

```{r}
# PhD Dissertation Committees
# tribble(
#   ~ year, ~ name, ~ role, ~ institution,
# ) %>%
#   detailed_entries(
#     when = year,
#     with = name,
#     what = role,
#     where = institution
#   )
```
-->

## Professional Development

```{r}
tribble(
  ~ year, ~ name, ~ program, ~ institution,
  '08/2025 - 05/2026', "Madison Teaching and Learning Excellence", "Center for Teaching, Learning, and Mentoring", "University of Wisconsin-Madison",
  '08/2025', "The Discussion Project", "Wisconsin Center for Education Research", "University of Wisconsin-Madison",
  '05/2025', "Wisconsin Idea Seminar", "Office of the Provost", "University of Wisconsin-Madison"
) %>%
  detailed_entries(
    when = year,
    what = name,
    with = program,
    where = institution
  )
```

# Service

<!--
## University

```{r}
# tribble(
#   ~ year, ~ name, ~ role, ~ institution,
# ) %>%
#   detailed_entries(
#     when = year,
#     with = name,
#     what = role,
#     where = institution
#   )
```
-->

<!--
## College

```{r}
# tribble(
#   ~ year, ~ name, ~ role, ~ institution,
# ) %>%
#   detailed_entries(
#     when = year,
#     with = name,
#     what = role,
#     where = institution
#   )
```
-->

## School of Journalism and Mass Communication Service

```{r}
tribble(
  ~ year, ~ name, ~ role, ~ institution,
  '01/2025 - Present', "Graduate Committee", "", ""
) %>%
  detailed_entries(
    when = year,
    with = name,
    what = role,
    where = institution
  )
```

## Disciplinary Service

```{r}
tribble(
  ~ year, ~ name, ~ duty,
  '01/2025 - Present', "International Journal of Press + Politics", "Data Editor",
  '09/2020 - Present', "Media & Democracy Data Cooperative (MDDC)", "Research Lead, Executive Board Member, https://mddatacoop.org/",
  '06/2023 - 06/2024', "International Communication Association Hackathon","Co-Organizer, https://www.hackingcommsci.org/",
  '12/2021 - 04/2022', "Digital Data Conference (D2C)", "Co-Organizer, https://mediaengagement.org/event/digital-data-conference/",
  '', "Peer-Reviewer", "AI and Ethics, Communication Methods and Measures, Computational Communication Research, Human Communication Research, Information Processing and Management, International Journal of Public Opinion Research, Journal of Online Trust and Safety, Journal of Quantitative Description: Digital Media, Mass Communication & Society, New Media & Society, Political Communication, Science Advances, Social Science Computer Review, Virtual Reality"
) %>%
  detailed_entries(
    when = year,
    with = name,
    what = duty
  )
```

# Professional Experience

```{r}
tribble(
  ~ title, ~ year, ~ company, ~ where, ~ details,
  "Data Scientist", "2018-2020", "Ovative Group", "Minneapolis, MN", "Full-stack Data Scientist coding in R, Python and SQL to build tools measure the causal mechanisms of digital media exposure on online and offline sales for brands such as UnitedHealth Group, Facebook Marketplace and Coach Bags",
  "Political Data Consultant", "2015-2024", "Self-Employed", "Madison, WI", "Built predictive models of voters for political campaigns using survey and voter contact data for state-wide, judicial, and municipal political campaigns using machine learning in R and Python. Models were used to allocate campaign budget, prioritize advertising audiences, and make strategic campaign decisions"
) %>%
  detailed_entries(company, year, title, where)
```
